A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-13 paper.tex
minor edits in Abstract

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% Background
Gradual typing combines dynamic typing and static typing in one
language to provide the advantages of both typing
disciplines. Implementing gradual typing with reasonable overhead,
however, is not trivial. Casts accumulate on higher-order values and
continuations, changing the overall space complexity. Several
space-efficient cast representations have been proposed, notably
coercions in normal forms and threesomes.
These cast representations shall be proved not changing the overall
behavior of language implementations except saving space.
Existing proofs typically go through a bisimulation between
a space-efficient semantics, which use a specific cast representation,
and the definitional but inefficient semantics \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
% Problem
However, this technique imposes unnecessary burden to proof writer
because a considerable portion of the semantics is irrelevant to
casts.
% Solution
To isolate cast representations from the remaining part of 
implementations, we present a abstract data type, namely Cast ADT,
that captures interface functions a cast representations typically 
includes, and an abstract machine parameterized over Cast ADTs.
Our generic dynamic semantics comes with generic theorems,
% Why is our solution a step forward
with which the correctness proofs can be done by just proving 
properties of a specific Cast ADT.
% %
% To isolate cast representations from the remaining part of 
% implementations, we present a abstract data type, namely Cast ADT,
% that captures interface functions a cast representations typically 
% includes, and an abstract machine parameterized over Cast ADTs.
% %
% With our generic abstract machine, the correctness proofs can be
% done by proving properties of a specific Cast ADT, which is simpler
% than proofs regarding the entire dynamic semantics.
%%%%%
% %
% But they are presented in
% different dynamic semantics, which make it difficult to compare the
% key differences between the cast representations.
% %
% We present a
% abstract data type, namely Cast ADT, that captures interface functions
% a cast representations typically includes, and an abstract machine
% parameterized over Cast ADTs.
% %
% The Cast ADT brings another benefit:
% space-efficient cast representations shall be proved not changing the
% overall behavior of language implementations except saving space.
% %
% With our generic abstract machine, these proofs can be done by proving
% properties of a specific Cast ADT, which is simpler than proofs
% regarding the entire dynamic semantics.
\todo[inline]{JS: The stuff above about ``make it difficult to compare''
  is a weak argument. I would recommend deleting that argument and
  instead focus on the benefits regarding the proofs of correctness.}
\todo[inline]{KC: updated.}

>>>>

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{Lu et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% Background
Gradual typing combines dynamic typing and static typing in one
language to provide the advantages of both typing
disciplines. Implementing gradual typing with reasonable overhead,
however, is not trivial. Casts accumulate on higher-order values and
continuations, changing the overall space complexity. Several
space-efficient cast representations have been proposed, notably
coercions in normal forms and threesomes.
These cast representations shall be proved not changing the overall
behavior of language implementations except saving space.
Existing proofs typically go through a bisimulation between
a space-efficient semantics, which use a specific cast representation,
and the definitional but inefficient semantics \citep{Siek:2010:TWB:1706299.1706342,Siek:2015:BCT:2737924.2737968}.
% Problem
This technique imposes unnecessary burden in proving such theorems
because a considerable portion of the semantics is irrelevant to
casts.
% Solution
To isolate cast representations from the remaining part of 
semantics, we present a abstract data type, namely Cast ADT,
that captures interface functions a cast representations typically 
includes, and an abstract machine parameterized over Cast ADTs.
Our generic dynamic semantics comes with generic theorems,
% Why is our solution a step forward
with which the correctness proofs can be done by just proving 
properties of a specific Cast ADT.
% %
% To isolate cast representations from the remaining part of 
% implementations, we present a abstract data type, namely Cast ADT,
% that captures interface functions a cast representations typically 
% includes, and an abstract machine parameterized over Cast ADTs.
% %
% With our generic abstract machine, the correctness proofs can be
% done by proving properties of a specific Cast ADT, which is simpler
% than proofs regarding the entire dynamic semantics.
%%%%%
% %
% But they are presented in
% different dynamic semantics, which make it difficult to compare the
% key differences between the cast representations.
% %
% We present a
% abstract data type, namely Cast ADT, that captures interface functions
% a cast representations typically includes, and an abstract machine
% parameterized over Cast ADTs.
% %
% The Cast ADT brings another benefit:
% space-efficient cast representations shall be proved not changing the
% overall behavior of language implementations except saving space.
% %
% With our generic abstract machine, these proofs can be done by proving
% properties of a specific Cast ADT, which is simpler than proofs
% regarding the entire dynamic semantics.
\todo[inline]{JS: The stuff above about ``make it difficult to compare''
  is a weak argument. I would recommend deleting that argument and
  instead focus on the benefits regarding the proofs of correctness.}
\todo[inline]{KC: updated.}
